\textsc{Second-order state-constraint Hamilton-Jacobi equations}

### 2021-05-03 Drafts and notes/Notes/Special_data.tex
New Draft with established results

\begin{center}
{\LARGE \textsc{Quasilinear equations}}\\
%{Từ Nguyễn Thái Sơn}\\
%{\setfont{calligra}{Son Nguyen Thai Tu}}\\
%{\setfont{frc}{March 13, 2021}}\\
{\textit{March 24, 2021}}
\end{center}

@@

\begin{enumerate}
    \item Try the special case $\Omega = B(0,1)$, note that we have $\Delta d(x) = 0$ in one dimension. Question: what is the difference between the rotational case (radial) vs one dimensional? 
    \item Try out the special case $f(x) = f(|x|)$ in $B(0,1)$, in which we can reduce it to one-dimensional setting.
    \item Try out the specific case $f(x) = 1-|x|$ on $(-1,1)$ and $f(x) = 0$ in $1\leq |x|\leq 2$ on the domain $\Omega = (-2,2)$. This is a simple case of the compactly supported data.
    \item Idea for general data: Assume $u^\varepsilon\to u$ as $\varepsilon\to 0$. We compare $u^\varepsilon$ and $v^\varepsilon$ where $1<p\leq 2$ and
\begin{equation}\label{eq:PDEeps}
    \begin{cases}
   \mathcal{L}[u^\varepsilon] =  u^\varepsilon(x) + |Du^\varepsilon(x)|^p - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
   u^\varepsilon(x) = +\infty &\qquad
    \text{on}\;\partial\Omega
    \end{cases} \tag{PDE$_\varepsilon$}
\end{equation}
and
\begin{equation}\label{eq:vPDEeps}
    \begin{cases}
   \mathcal{L}[v^\varepsilon] =  v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) - \varepsilon \Delta v^\varepsilon(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
   v^\varepsilon(x) = u(x) &\qquad
    \text{on}\;\partial\Omega.
    \end{cases} 
\end{equation}
We know that $|v^\varepsilon - u|\leq C\sqrt{\varepsilon}$, thus the goal is to compare $u^\varepsilon$ and $v^\varepsilon$. Let $w^\varepsilon(x) = u^\varepsilon(x) - v^\varepsilon(x)$, we have
\begin{equation}\label{eq:wPDEeps}
    \begin{cases}
w^\varepsilon(x) + |Du^\varepsilon(x)|^p  - |Dv^\varepsilon|^p - \varepsilon \Delta w^\varepsilon(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
   w^\varepsilon(x) = +\infty &\qquad
    \text{on}\;\partial\Omega.
    \end{cases} 
\end{equation}
The good thing about \eqref{eq:wPDEeps} is, the data $f$ disappears and furthermorethe new data, for example with $p=2$ can be written as
\begin{equation}\label{eq:wwPDEeps}
    \begin{cases}
w^\varepsilon(x) + |Dw^\varepsilon(x)|^2 +\underbrace{2Dw^\varepsilon(x)\cdot Dv^\varepsilon(x)}_{g
(x)} - \varepsilon \Delta w^\varepsilon(x) = 0 &\qquad
    \text{in}\;\Omega, \vspace{0cm}\\
   w^\varepsilon(x) = +\infty &\qquad
    \text{on}\;\partial\Omega.
    \end{cases} 
\end{equation}
and $g(x) \approx \frac{\varepsilon \nabla d(x)\cdot \nabla v^\varepsilon(x)}{d(x)} + |Dv^\varepsilon(x)|^2$, which is small in some sense depends on $\varepsilon$. Question: can we get a rate of convergence $w^\varepsilon(x)\to 0$? What is the behavior of $Dv^\varepsilon(x)$ as $\varepsilon\to 0$? Can we know more besides $|v^\varepsilon - u|\leq C\sqrt{\varepsilon}$?
\item Building a better supersolution for compactly supported data. Using the above $v^\varepsilon$ in \eqref{eq:vPDEeps}, can we somehow show
\begin{equation*}
    u^\varepsilon(x) \leq v^\varepsilon(x) + \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} 
\end{equation*}
in $\Omega$ when we assume $\mathrm{supp}\;f \subset \Omega_{\delta_0}$? 
\item Showing $u^\varepsilon$ is very small in the region where $f = 0$, for example $\mathrm{supp}\;f \subset \Omega_{\delta_0}$, using stochastic control. The idea behind this is, $u(x) = 0$ whenever $f(x) = 0$ (we assume $f\geq 0$) and $u^\varepsilon\to u$, thus $u^\varepsilon$ has to be very small where $f = 0$, thus there is a hope to build a better supersolution, to show that 
\begin{equation*}
       u^\varepsilon(x) \leq \frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} 
\end{equation*}
where $x$ in the region where $f(x) = 0$. Specifically, solution $u^\varepsilon$ to \eqref{eq:PDEeps} can be written as
\begin{equation*}
    u^\varepsilon(x) = \inf_{a(\cdot)\in \mathcal{A}}  \mathbb{E}\left[\int_0^\infty e^{-t}\left(\frac{(\alpha+1)^{\alpha+1}}{(\alpha+2)^{\alpha+2}}|a(X_t)|^{\alpha+2} + f(X_t)\right)dt \right]
\end{equation*}
where $q = \alpha+2$ satisfies $\frac{1}{q} + \frac{1}{p} = 1$, where
\begin{equation*}
    \begin{cases}
    dX_t = a(X_t)dt + \varepsilon\sqrt{2} d\mathbb{B}_t\\
    \;\;X_0 = x
    \end{cases}
\end{equation*}
and $\mathcal{A}$ is the set of continuous function $a(\cdot):\Omega \to \mathbb{R}$ such that the state $X_t\in \overline{\Omega}$ with probability 1 for all time $t\geq 0$ and for all initial points $x\in \Omega$. Here $\mathbb{B}_t$ is the standard Brownian motion. The hope is that, the optimal Markovian control is given by
\begin{equation*}
    a_0(x) = p|\nabla u^\varepsilon(x)|^{p-2}\nabla u^\varepsilon(x).
\end{equation*}
Hence, note that
\begin{equation*}
    \frac{1}{qp^{\alpha+1}} = \frac{(\alpha+1)^{\alpha+1}}{(\alpha+2)^{\alpha+2}}
\end{equation*}
we have
\begin{equation*}
   \frac{1}{qp^{\alpha+1}} |a_0(X_t)|^q =  \frac{1}{qp^{\alpha+1}}p^q |\nabla u^\varepsilon(x)|^p = \frac{1}{pq}|\nabla u^\varepsilon(x)|^p \approx \frac{1}{pq}\frac{(C_\alpha \alpha)^p\varepsilon^{\alpha+2}}{d(x)^{\alpha+2}}.
\end{equation*}
In fact, this estimate can be make rigorously from \cite{alessio_asymptotic_2006}, that is there is a constant $C>0$ such that
\begin{equation*}
    |\nabla u ^\varepsilon(x)|\leq \frac{C\varepsilon^{\alpha+1}}{d(x)^{\alpha+1}}
\end{equation*}
for $x\in \Omega$.
\end{enumerate}

%\bibliography{zzzzlibrary}{}
%\bibliographystyle{ieeetr}
%\bibliographystyle{acm}
\end{document}

>>>>

\begin{center}
{\LARGE \textsc{Special data}}\\
%{Từ Nguyễn Thái Sơn}\\
%{\setfont{calligra}{Son Nguyen Thai Tu}}\\
%{\setfont{frc}{March 13, 2021}}\\
{\textit{April 09, 2021}}
\end{center}

@@

\section{General case}
Let us consider $p = 2$ and $\delta_0>0$ such that $d(x) = \mathrm{dist}(x,\partial\Omega)$ for $x$ near the boundary such that $0<d(x)<\delta_0$. We extend $d(\cdot)\in \mathrm{C}^2(\mathbb{R}^n)$. We consider the equation:
\begin{equation}\label{eq:PDEeps}
    \begin{cases}
   \mathcal{L}[u^\varepsilon] =  u^\varepsilon(x) + |Du^\varepsilon(x)|^2 - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
    \text{in}\;\Omega, \vspace{0cm}\\
    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty.
    \end{cases} \tag{PDE$_\varepsilon$}
\end{equation}
Let $K_0 = \Vert d\Vert_{L^\infty}, K_1 = \Vert\nabla d\Vert_{L^\infty}$ and $K_2 = \Vert \Delta d\Vert_{L^\infty}$. We summarize some results from \cite{Lasry1989} in a clearer manner here for convenience. Let us without loss of generality assume $f\geq 0$ a.e. in $\Omega$ (\textit{positivity}). 
\begin{enumerate}
    \item If $f = 0$, we are good to go, as 
    \begin{equation}\label{e:spirit}
        u(x) = \frac{\nu C_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha} + \left(\frac{C\varepsilon^{\alpha+2}}{\delta_{0,\Omega}^{\alpha+2}}\right)
    \end{equation}
    is a supersolution. 
    \item If $f$ is compactly supported in $\Omega_\kappa$ we are good to go as well.
    \item Instead, if $f$ is a constant we should be able to do the same. Can we improve the result to the case that $f$ is constant in the strip $\Omega\backslash \overline{\Omega}_\kappa$?
    \item Now here is the deal, in the spirit of \eqref{e:spirit} above, we see that when we plug in the solution $u$ from \eqref{e:spirit} into the equation, we simply ignore the contribution of the monotone term $u(x)$, even though it is positive. That leads to the following observation, if we choose 
    \begin{equation*}
        f(x) =  \frac{\theta C_\alpha\varepsilon^{\alpha+1}}{d(x)^\alpha}, \qquad x\in \Omega
    \end{equation*}
    for any $\theta > 1$ then clearly
    \begin{equation*}
        \mathcal{L}^\varepsilon[\theta u] \geq 0
    \end{equation*}
    therefore $\theta u$ from \eqref{e:spirit} is still a supersolution. While if $\theta\leq 1$, we simply use $u$ as a supersolution. Furthermore, if 
    \begin{equation*}
    \fbox{$\displaystyle    f(x) = \frac{\theta C_\alpha\varepsilon^{\alpha+1}}{d(x)^\beta} $}
    \end{equation*}
    for any $0<\beta\leq \alpha$ this argument still works. Can we still have a rate of convergence?
\end{enumerate}

\bibliography{zzzzlibrary}{}
%\bibliographystyle{ieeetr}
\bibliographystyle{acm}
\end{document}

### 2021-05-03 Drafts and notes/Things to try.tex
New Draft with established results

@@

%\bibliography{zzzzlibrary}{}
%\bibliographystyle{ieeetr}
%\bibliographystyle{acm}
\end{document}

>>>>

\item Idea to bound point-wise $u^\varepsilon(x)$ without using stochastic formula. If $x\in \Omega$ such that we can find $r>0$ such that $B(x,r)\subset \{f = 0\}$ then by consider an explosive solution $w^\varepsilon$ in $B(x,r)$, then as $w^\varepsilon\to 0$ in $B(x,r)$ and $u^\varepsilon \leq w^\varepsilon$ in $B(x,r)$, one can get a rate locally for $u^\varepsilon$ if we can control the radius $r$, provided we know the support of $f$. \textcolor{red}{This idea is clear, probably no more explanation needed or further investigation, maybe?}
\item Difficulty for the general case of bounded data $f$, after cutting off $f_\kappa = f\chi_\kappa$ such that $\mathrm{supp}(f_\kappa)\subset \Omega_\kappa$, the solution of the corresponding problem is $u^\varepsilon_\kappa$ which is not exactly $u^\varepsilon$, eventhough $u^\varepsilon_\kappa\to u^\varepsilon$ as $\kappa \to 0$. However the rate exploded when $\kappa \to 0$ unless we choose a scale $\kappa = \varepsilon^\gamma$ for $\gamma < 1$, but then in the equation $u^\varepsilon_\kappa\to u^\varepsilon$ we loose the term $\varepsilon$ here. 
\begin{itemize}
    \item An idea to try: bound in the interior only. Write
        f = \frac{1}{2}\left( \underbrace{\qquad\qquad 2f\chi_\kappa\qquad\qquad}_{f_1 \longrightarrow u^\varepsilon_1} +  \underbrace{\qquad\qquad 2f(1-\chi_\kappa)\qquad\qquad}_{f_2 \longrightarrow u^\varepsilon_2}\right).
    We know $u_1^\varepsilon\to 0$ with a rate everywhere, while $u_2^\varepsilon \to 0$ in $\Omega_\kappa$ with a rate, thus by convex combination we maybe able to control a rate for $u^\varepsilon$ in $\Omega_\kappa$. \textcolor{red}{Seems wrong! As we only have subsolution, not supersolution.}
\end{itemize}

@@

\begin{center}
--------------------------------------------------------------------------------------------------------------------
\end{center}
\begin{enumerate}
    \item \textcolor{blue}{Log April 03, 2021.} Figured out the annulus bound enables a proof for compactly supported data.
\end{enumerate}

\bibliography{zzzzlibrary}{}
%\bibliographystyle{ieeetr}
\bibliographystyle{acm}
\end{document}
